A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-19 MSRChallenge2016.tex
Added median and github link

\vspace{1ex}
\noindent\textbf{How many files are changed to fix a bug?}
%
We consider a file changed if it is new, modified, or
deleted in a commit. In total, $52,052,571$ files were changed, an average of 
$11.3$ files per bug-fixing commit.  This is surprisingly high:
most automatic program repair techniques assume that bugs are local.
We hypothesize several explanations: Other
software artifacts (e.g.  documentation) may be updated after bug  
fixing, or fixing commits may contain changes
unrelated to fixing the bug (e.g. refactoring, feature addition). 
To better understand this
phenomenon, we ask:

\begin{table}
\centering
  \begin{tabular}{ l | r  r }
  \toprule
  File Kind & Total & Average \\ 
  \midrule
  Binary & 752,945 & 0.16 \\ 
  Java (ERROR) & 2,073,558 & 0.45 \\ 
  Java (JLS2) & 2,607,413 & 0.57 \\ 
  Java (JLS3) & 15,748,967 & 3.43 \\
  Java (JLS4)  & 83,798 & 0.02 \\ 
  Text & 541,023 & 0.12 \\ 
  XML & 6,818,299 & 1.49 \\ 
  UNKNOWN & 23,426,568 & 5.10 \\ 
\bottomrule
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:fileType}
\end{table}
\vspace{1ex}
\noindent\textbf{What are the types of those changed files?}
%
To answer this question, we iterate over all changed files in each bug fixing
revision and count the total number for each file type. Results are shown in
Table~\ref{tbl:fileType}.
%
JAVA (ERROR) files are those that Boa failed to parse. JLS2,
JLS3, and JLS4 represent Java files written in different J2SE versions.  We see that text and Binary files are
changed least frequently. This is unsurprising, since text files are often
documentation, and binaries should only be changed rarely. If we consider all 4 kinds of Java
files as one kind, on average, each bug fixing revision changes $4.47$ Java
files. This still does not conform to our assumption of bug locality. XML
files in Java projects usually represent build files; changing a build
file is unsurprising.  Rather more surprising is how frequently UNKNOWN files
are changed. Given that all the projects are Java projects, 
it is unclear whether these are written in other proramming
languages. We hypothesize they might be test resources.
\todo{possibly mention median, if Chu Pan gets that information}
To better understand what changes are usually made to Java source code
files, we next ask:

@@

% \todo{Is there room/call to include any element of Chu Pan's replacement
%   analysis in here?}

@@

\noindent\textbf{Threats to validity.} Since we are using a DSL
provided by Boa, the correctness of our analysis
depends on both our programs and Boa itself. For example, we rely on Boa to
identify bug fixing revisions; however, precisely accomplishing this is an open
problem.  To mitigate the risk of errors in
implementation, we open source our scripts~\footnote{\todo{FIX THIS NOW}}.
Because Boa does not provide an easy mechanism
to identify precise, statement-level diffs between revisions, our template
matching and analysis of code changes (by counting each statement kind) only
provide estimates of behavior; we consider our results as informative
approximations.

>>>>

\vspace{1ex}
\noindent\textbf{How many files are changed to fix a bug?}
%

We consider a file changed if it is new, modified, or deleted in a commit. In
total, $52,052,571$ files were changed, an average of $11.3$ files per
bug-fixing commit, and the median number is $2$.  Although the median number
conforms to our intuition, the average is surprisingly high: most automatic
program repair techniques assume that bugs are local.  We hypothesize several
explanations: Other software artifacts (e.g.  documentation) may be updated
after bug  fixing, or fixing commits may contain changes unrelated to fixing
the bug (e.g.  refactoring, feature addition).  To better understand this
phenomenon, we ask:

\begin{table}
\centering
  \begin{tabular}{ l | r  r }
  \toprule
  File Kind & Total & Average \\ 
  \midrule
  Binary & 752,945 & 0.16 \\ 
  Java (ERROR) & 2,073,558 & 0.45 \\ 
  Java (JLS2) & 2,607,413 & 0.57 \\ 
  Java (JLS3) & 15,748,967 & 3.43 \\
  Java (JLS4)  & 83,798 & 0.02 \\ 
  Text & 541,023 & 0.12 \\ 
  XML & 6,818,299 & 1.49 \\ 
  UNKNOWN & 23,426,568 & 5.10 \\ 
\bottomrule
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:fileType}
\end{table}
\vspace{1ex}
\noindent\textbf{What are the types of those changed files?}
%
To answer this question, we iterate over all changed files in each bug fixing
revision and count the total number for each file type. Results are shown in
Table~\ref{tbl:fileType}.
%

JAVA (ERROR) files are those that Boa failed to parse. JLS2, JLS3, and JLS4
represent Java files written in different J2SE versions.  We see that text and
Binary files are changed least frequently. This is unsurprising, since text
files are often documentation, and binaries should be changed rarely. If we
consider all 4 kinds of Java files as one kind, on average, each bug fixing
revision changes $4.47$ Java files. This does not conform to our assumption of
bug locality. XML files in Java projects usually represent build files;
changing build files is unsurprising.  Rather more surprising is how frequently
UNKNOWN files are changed. Given that all projects are Java projects, it is
unclear whether these are written in other programming languages. We
hypothesize they might be test resources.  To better understand what changes
are usually made to Java files, we next ask:

@@

@@

\noindent\textbf{Threats to validity.} Since we are using a DSL
provided by Boa, the correctness of our analysis
depends on both our programs and Boa itself. For example, we rely on Boa to
identify bug fixing revisions; however, precisely accomplishing this is an open
problem.  To mitigate the risk of errors in
implementation, we open source our scripts~\footnote{\url{https://github.com/chupanw/BoaChallenge}}.
Because Boa does not provide an easy mechanism
to identify precise, statement-level diffs between revisions, our template
matching and analysis of code changes (by counting each statement kind) only
provide estimates of behavior; we consider our results as informative
approximations.
